### 2024-07-01 analysis/analysis.qmd
analysis ideas updated

- [ ] CA ToDo: Check the warning reported here

@@

- [x] Issue 1: We need unique identifiers for each input component (combine: `study` + `model` + `feature` + `data` + `experiment` that would have be unique id)
- [x] Issue 2: We `stimulus_N`
- [x] Issue 3: measure vs statistic?
- [x] Issue 4: We need to classify the modelling techniques into fewer number of techniques (example given, but no principles defined)
- [ ] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)

@@

#### Valence

@@

# Temporary clarification of N
tmp$stimulus_n[tmp$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "]<-1000
tmp$stimulus_n[tmp$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "]<-2372
tmp$stimulus_n[tmp$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "]<-40
tmp$stimulus_n <- as.numeric(tmp$stimulus_n)

@@

m.cor <- metacor(cor = sqrt(values), 
                 n = stimulus_n,
                 studlab = citekey,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: All")

@@

# divide models into random forests, SVM and MLR
tmp$model_class_id <- 'MLR/PLS'
tmp$model_class_id[str_detect(tmp$model_id,'RFR|extremely randomized tree regression')]<-'RF'
tmp$model_class_id[str_detect(tmp$model_id,'svm|SVR')]<-'SVM'
table(tmp$model_class_id)
meta <- metagen(values, sqrt(values), # Fix the TE.se 
                data = tmp, 
                studlab = tmp$citekey, 
                comb.fixed = FALSE, 
                method.tau = "PM")

@@

>>>>

@@

- [x] Issue 1: We need unique identifiers for each input component (combine: `study` + `model` + `feature` + `data` + `experiment` that would have be unique id)
- [x] Issue 2: We `stimulus_N`
- [x] Issue 3: measure vs statistic?
- [ ] Issue 4: We need to classify the modelling techniques into fewer number of techniques (example given, but no principles defined)
  - Possible solution from "Dive into Deep Learning" by Zhang et al., 2024
    1. Linear Neural Networks
    2. Recurrent Neural Networks
    3. Convolutional Neural Networks
    4. Attention mechanisms (probably not applicable here, these are LMMs)

- [x] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)

```{r}
#| echo: false
#| eval: true
library(stringr)
metaMER_results$studyREF <- substr(metaMER_results$citekey,1,nchar(metaMER_results$citekey)-2)
metaMER_results$studyREF <- str_replace_all(metaMER_results$studyREF,'([0-9]+)',' et al \\1')
metaMER_results$studyREF <- str_to_sentence(metaMER_results$studyREF)
```

@@

#### Valence: all models, datasets, features

@@

# Temporary clarification of N
tmp$stimulus_n[tmp$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "] <- 1000
tmp$stimulus_n[tmp$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "] <- 2372
tmp$stimulus_n[tmp$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "] <- 40
tmp$stimulus_n[tmp$stimulus_n==" MER60: 60, CH818: 818, AMG1608: 1608  "] <- 818
tmp$stimulus_n <- as.numeric(tmp$stimulus_n)

@@

m.cor <- metacor(cor = sqrt(values), 
                 n = stimulus_n,
                 studlab = studyREF,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: All")

@@

# Classify techniques according Hastie, Tibshirani, Friedman (2008)
#
# https://www.sas.upenn.edu/~fdiebold/NoHesitations/BookAdvanced.pdf
#
# 3. Linear Methods for Regression
# 4. Linear Methods for Classification 
# 5. Basis Expansions and Regularization
# 6. Kernel Smoothing Methods
# 7. Model Assessment and Selection
# 8. Model Inference and Averaging 
# 9. Additive Models, Trees, and Related Methods
# 10. Boosting and Additive Trees
# 11. Neural Networks
# 12. Support Vector Machines and Flexible Discriminants
# 15. Random Forests
# 16. Ensemble Learning

# divide models into random forests, SVM and MLR
table(tmp$model_id)
tmp$model_class_id <- 'Unclassified'
tmp$model_class_id[str_detect(tmp$model_id,'lr|lm')] <- 'LR' # CAM?
tmp$model_class_id[str_detect(tmp$model_id,'PLS|MLR|gaussian|gmm|GMM|mlr|PLSR|sparse|variational bayesian')]<-'MLR/PLS'
tmp$model_class_id[str_detect(tmp$model_id,'RFR|extremely randomized tree regression|forest|rfr')]<-'RF'
tmp$model_class_id[str_detect(tmp$model_id,'svm|SVR|svr')]<-'SVM'
tmp$model_class_id[str_detect(tmp$model_id,'rnn')]<-'RNN'
tmp$model_class_id[str_detect(tmp$model_id,'bee|backprop|knn|mars|rbf|smoreg')]<-'NN other'
table(tmp$model_id,tmp$model_class_id)
tmp$model_class_id<-factor(tmp$model_class_id)

meta <- metagen(values, sqrt(values), # Fix the TE.se 
                data = tmp, 
                studlab = tmp$studyREF, 
                comb.fixed = FALSE, 
                method.tau = "PM")

@@

## Take the max from each study

Also max and min.

Idea: visualise the distributions of the model successes within studies

```{r}

g <- ggplot(tmp,aes(y=values,fill=model_class_id))+
  geom_histogram(show.legend = T)+
  facet_wrap(.~studyREF)+
  coord_flip()+
  theme_bw()
g

# S <- summarise(group_by(tmp,citekey),maxvalue=max(values))
# g<-ggplot(S,aes(y=maxvalue))+
#   geom_histogram(bins = 14)+
#   #facet_wrap(.~studyREF)+
#   coord_flip()+
#   theme_bw()
# g

## Plot success across the years
